\documentclass[../../main.tex]{subfiles}
\begin{document}
\setcounter{footnote}{0} 
\newcommand{\rom}[1]{\uppercase\expandafter{\romannumeral #1\relax}}


\chapter{Machine Learned Potentials}

\section{Overview}

Although DFT remains steadfast as the computational method of choice to study reactions of more than a few atoms,\cite{PribramJones2015} there remain significant limitations in speed and accuracy.\cite{Mardirossian2017} For example, while a DFT estimate of the catalytic activity of a metallocage may be obtained in a day\cite{Young2019} (faster than the corresponding experiment), efficient methods are required for high-throughput virtual screening. Moreover, absolute barrier heights are rarely within 5 \kcalx of the true value (e.g. ref. \cite{Krongchon2017}). Therefore, a predictive computational approach to catalyst design using enumerative \emph{ab initio} calculations requires faster access to accurate absolute energies. 

Accurate inclusion of solvent effects is also a long-standing challenge, with solvation free energy errors in the 5 \kcalx range for neutral and $>$5 \kcalx for charged species.\cite{Takano2004, Zhang2017} Inclusion of solvent effects capturing directional interactions missing from implicit models require either cluster-continuum models or QM/MM. The former often lacks sufficient sampling and/or convergence with respect to the number of explicit solvents,\cite{Basdogan2018} while the latter also suffers from how to couple the regions, and forcefield accuracy.\cite{Thiel2009} Methods that could calculate total periodic system energies quickly would thus alleviate these problems and enhance accuracy where solvent effects are appreciable.

Reaction dynamics can also be important in (catalytic) reactions,\cite{Grajciar2018, Stirling2014} but generally require computationally expensive AIMD. Therefore the accuracy is generally cannot limited to the GGA DFT-level in the condensed phase.\cite{Hassanali2014} Methods to rapidly generate energies and forces that are reactive and accurate would increase the understanding these processes.

Manuscript \rom{4} outlines a route to developing bespoke machine learned potentials capable of delivering energies and forces in $O(\text{ms})$ for a wide range of systems. Using a Gaussian Approximation Potential framework,\cite{Bartok2010} hyperparameters and a method of generating reference configurations were developed so an ML potential can be trained for a variety of systems in a day or so. This method enabled CCSD(T)-quality dynamics for an S${}_\text{N}$2 reaction, accurate bulk (periodic) water simulations using hybrid DFT and reactive dynamics of a condensed phase reaction. The training method is also applicable to reaction discovery; by initialising velocities sufficient to make/break bonds, an exothermic S${}_\text{N}$2 reaction was sampled from an association complex of reactants.

The method and freely available code ({\url{https://github.com/t-young31/gap-train}}) will enable more routine development of ML potentials where, for example, possible bifurcations occur and barrier heights are insufficient to predict selectivity.\cite{Feng2021} Solvent effects can be interrogated using this method and a GGA DFT-quality potential generated within a day. It is also applicable to finding intermediates and transition states of new reactions. However, the generated potentials are intrinsically bespoke and thus limited in transferability. Therefore, more data-intensive approaches are likely to prevail in this domain.\cite{Smith2017, Devereux2020} 


\clearpage
\end{document}